---
title: "Notes from the git course"
author: "Marie-Pierre Etienne"
date: "July 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#  git generalities 

## Hidden variables in R

if you create a variable `.hidden <- 5` it's hidden.
```{r}
.hidden <- 4
ls()
.hidden + 2 
```


## Two camps in R
comit or not the Rproj
C. Gillepsie suggests to commit .Rproj


It may be a good idea to store the documentation of a package even if it is generated.

## more on .gitignore

see.gitignore of thr rpkg repo

# Travis

##  Building the package
CTRL + Shift + B

before submitting you have to check it 

checking the package
CTRL + Shift + E

select the package in travis


## PAT personnal authentification on github

github limits the number of request to 5000hour per hour. might occur some failures in the compilation with travis. 
To avoid this problem, we should use an identification to avaoid travis to use general identification. To do so create a persoannal authentification on github and with no right and inditaes it to travis 

should avoid error 403 problem.

## Working with multiple version of R
to check compatibility with different version

give access

